---
title: "A presentation on something incredibly interesting with `R`"
subtitle: "And something less"
date: "`r format.Date(Sys.Date())`"
author: "A. N. Onymous"
institute: "Methodology & Innovation in Official Statistics"
output: 
  beamer_presentation:
#    template: ~/.pandoc/templates/default.beamer
    theme: "estat"
#    includes:
#      in_header: extra.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## A slide with a dumb title longer than it should reasonably be

1. Item 1
2. Item 2
3. Item 3, as interesting as previous items
4. the longest item yet, even longer than the one above, though why you would want to make it that long is just another matter



 
## A slide with images

\begin{columns}[totalwidth=\textwidth,T]
  \begin{minipage}{0.45\textwidth}
    \begin{column}[t]{\textwidth}
      \centering
      what can we say about \\[0.5cm]
      \includegraphics[width=\textwidth]{../imgs/eurostat_logo.png}
    \end{column}
  \end{minipage}
  \begin{minipage}{0.45\textwidth}
    \begin{column}[t]{\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../imgs/juncker.png}\\[0.5cm]
      amazing... 
    \end{column}
  \end{minipage}
\end{columns}


## A frame with tasty multifractals

Let $\epsilon_r(\vec{x})$ be the local dissipation of energy at a point $\vec{x}$ over a ball $B_r(\vec{x})$  of radius r centered around $\vec{x}$, $v_i$  the components of the velocity vector:

\begin{equation*} 
\epsilon_r(\vec{x}) = \frac{1}{\mid B_r(\vec{x})\mid}
\int_{B_r(\vec{x})}
d\vec{x'} \sum_{i,j} [  \delta_i v_j(\vec{x'}) + \delta_j v_i(\vec{x'}) ]
\end{equation*}

Under self-similarity assumptions, energy is transmitted from the larger scales ($L$) to the smaller ones ($r$) by means of an injection process which  only depends on the ratio $r/L$, and all the dependence in $r$ of the order-$p$ moment of $\epsilon_r$ is concentrated in the power-law

\begin{equation*} 
\langle \epsilon_r \rangle = \Big[ \frac{r}{L} \Big]^{-\alpha p}  \langle \epsilon^p_L\rangle \propto  r^{\tau_p} 
\end{equation*}

## Finally some R code

R rocks!
```{r cars, echo = TRUE}
summary(cars)
```
